ChemKED: a human- and machine-readable data standard for chemical kinetics experiments

### 2017-02-26 pyked.tex
Edit conclusion

    print('The ignition delay for T_0={}, P_0={} is: {} seconds'.format(
        T_0, P_0, netw.time
    ))
\end{pythonbox}
%
Note that the ignition delay in this example is defined as equal to $T_0 +
400\,\mathrm{K}$, a simplified definition used for this example. In general, the
user could post-process the concentration information from the simulation to
determine one-half the maximum OH* concentration to match the experimental
definition of ignition delay.
%====================================================================
\section{Conclusions and future work}
%
\todo[inline]{both to do}

In this article, we introduced the \ck{} data format for describing measurements
taken from fundamental combustion experiments, as well as the Python-based tool
\pk{} for working with the format. Currently, \ck{} supports ignition delay data
from studies using shock tubes and rapid compression machines.

We are currently incorporating support for specifying uncertainty in all quantities.
Version 1.0 of \ck{}\slash \pk{} will include ...
Later versions will support measurements from additional fundamental experiments,
including laminar flames and flow reactors.

>>>>

    print('The ignition delay for T_0={}, P_0={} is: {} seconds'.format(
        T_0, P_0, netw.time
    ))
\end{pythonbox}
%
Note that the ignition delay in this example is defined as equal to $T_0 +
400\,\mathrm{K}$, a simplified definition used for this example. In general, the
user could post-process the concentration information from the simulation to
determine one-half the maximum OH* concentration to match the experimental
definition of ignition delay.
%====================================================================
\section{Conclusions and future work}

Recognizing that the community has a need for an open and standardized data
serialization format, in this paper we have presented the \ck{} data format for
describing measurements taken from fundamental combustion experiments. \ck{}
files are formatted using the YAML language and are plain-text, human- and
machine-readable, and easy to construct.

We have also presented a Python-based tool, \pk{}, for validating and working
with \ck{} files. \pk{} provides the reference implementation of the validator
for \ck{} files and utilizes several common packages from Python's scientific
computing community. \pk{} and \ck{} currently support ignition delay
measurements from rapid compression machines and shock tubes, including facility
specific effects from each type of experiment.

\ck{} and \pk{} are currently under active development, and contributions from
the community are gratefully welcomed. All development occurs under the BSD
3-clause license and the code is housed on GitHub at
\url{https://github.com/pr-omethe-us/PyKED}. Future directions for development
are outlined in the public
\href{Roadmap}{https://github.com/pr-omethe-us/PyKED/wiki/Roadmap}. The highest
priority issues are currently adding support for other types of fundamental
experiments, including flame speed, speciation, and flame extinction
measurements.
